XOR-Some Prolific Pilot 1

### 2021-03-25 analysis/xor-some-prolific-pilot1.Rmd
knit analysis draft
minor fix

Next, we would exclude participants based on their ratings in the main / example trials (and possibly the bot check) according to preregistered exclusion criteria. For now, all the data is considered.
```{r clean}
d_native %>% group_by(submission_id) %>% count(response) %>% View()
d_main <- d_native %>% filter(trial_name != "example")
d_exmpl <- d_native %>% filter(trial_name == "example")
d_critical <- d_main %>% filter(condition == "critical")

@@

```{r}
d_critical <- d_critical %>% 
  pivot_longer(c(competence, relevance, prior), 
               names_to = "class_condition", 
               values_to = "prior_class")
d_critical %>% 
  filter(block != "xor" & block != "some") %>%
  ggplot(., aes(x = as.factor(prior_class), y = response)) +
  geom_point(size = 2, alpha = 0.3, position = position_jitter(width = 0.1)) +
    facet_wrap(main_type~class_condition)
```
Plot main rel / comp questions by main condition, separated into with / without critical utterance
```{r}
# add info to already record this
d_critical <- d_critical %>% 
  mutate(w_utterance = ifelse(is.na(critical_question), F, T),
         block = ifelse(block == "comp", "competence", 
                        ifelse(block == "rel", "relevance", "prior")))

@@

# some condition was wrongly recorded as pri
d_critical %>% 
     filter(block != "xor" & block != "some") %>%
     filter(block == class_condition) %>% filter(block == "prior" & w_utterance == T) %>% View()

```

>>>>

Next, we would exclude participants based on their ratings in the main / example trials (and possibly the bot check) according to preregistered exclusion criteria. For now, all the data is considered.
```{r clean}
d_native %>% group_by(submission_id) %>% count(response)
d_main <- d_native %>% filter(trial_name != "example")
d_exmpl <- d_native %>% filter(trial_name == "example")
d_critical <- d_main %>% filter(condition == "critical")

@@

```{r}
d_critical <- d_critical %>% 
  pivot_longer(c(competence, relevance, prior), 
               names_to = "class_condition", 
               values_to = "prior_class")
d_critical %>% 
  filter(block != "xor" & block != "some") %>%
  ggplot(., aes(x = as.factor(prior_class), y = response)) +
  geom_point(size = 2, alpha = 0.3, position = position_jitter(width = 0.1)) +
    facet_wrap(main_type~class_condition)
```
Plot main rel / comp questions by main condition, separated into with / without critical utterance
```{r}
# add info to already record this
d_critical <- d_critical %>% 
  mutate(w_utterance = ifelse(is.na(critical_question), F, T),
         block = ifelse(block == "comp", "competence", 
                        ifelse(block == "rel", "relevance", ifelse(block == "pri", "prior", block) )))

@@

# # some condition was wrongly recorded as pri
# d_critical %>% 
#      filter(block != "xor" & block != "some") %>%
#      filter(block == class_condition) %>% filter(block == "prior" & w_utterance == T) %>%
#   View()

d_critical %>% 
  filter(block != "xor" & block != "some") %>%
  filter(block == class_condition) %>%
  group_by(main_type, class_condition, w_utterance, prior_class) %>% 
  summarize(mean_response = mean(response))
```
